---
title: "DTA_L15_Plotly"
author: "Joy Hsu"
date: "10/23/2018"
output: html_document
---

### Lecture

* Dashboards
    * Ex. fitbit, investing platform, finances
    * most useful in the context of changing data. Data is changing, but structure of the platform is static
    
* flexdashboard
    * works with shiny
    * 

### 0. Setup

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(plotly)
```

Install airbnb dataset, cleanup
```{r}
set.seed(1)

data(nyc_airbnb)
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(boro = neighbourhood_group, neighbourhood, rating, price, room_type,
         latitude, longitude) %>%
  filter(!is.na(rating), 
         boro == "Manhattan",
         room_type == "Entire home/apt",
         price %in% 100:500)  %>% 
  sample_n(5000)
```

### 1. Plotly scatterplot

* scatterplot of nyc airbnb rentals, longitude and latitude
* interactivity

```{r}
#mutate step - 
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, '\nRating: ', rating)) %>% 
  plot_ly(x = ~longitude, y = ~latitude, type = "scatter", mode = "markers",
          alpha = 0.5, 
          color = ~price,
          text = ~text_label)
```

### 2. Boxplots

```{r}
#obtain list of top 8 neighborhoods
common_neighborhoods =
  nyc_airbnb %>% 
  count(neighbourhood, sort = TRUE) %>% 
  top_n(8) %>% 
  select(neighbourhood)

#left_join to filter nyc_airbnb dataset with only the top 8 most common neighborhood
inner_join(nyc_airbnb, common_neighborhoods,
             by = "neighbourhood") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box",
          colors = "Set2")
```

### 3. Barplot

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar")
```

### 4. ggplotly

Steps
  1. create plot using ggplot, save
  2. call ggplotly on scatterplot

* generally, using plotly directly is faster than creating ggplot and converting to plotly graphic
```{r}
scatter_ggplot = 
  nyc_airbnb %>%
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = 0.25) +
  scale_color_viridis() +
  coord_cartesian() +
  theme_classic()

ggplotly(scatter_ggplot)
```

### 5. flexdashboard

* see template script for flexdashboard
* copy and paste into flexdashboard template
* Column {data-width=650}, flexdashboard automatically assumes width of 1000, can partition as needed

```{r}

```

